Language and vision in conceptual processing: Multilevel analysis and statistical power

### 2022-09-26 manuscript/appendix-A-lexical-covariates.Rmd
26092022

# This appendix is rendered by the main manuscript. It inherits the 
# working directory and all the objects loaded in the main manuscript.

@@

Lexical covariates are usually used in conceptual processing studies due to the widespread connections among lexical and semantic variables. Including these covariates---or nuisance variables---in the model allows a more rigorous analysis of the predictors of interest [@sassenhagenCommonMisapplicationStatistical2016].

In each study, the covariates were selected out of a group of 5 variables that had been used as covariates in @wingfieldUnderstandingRoleLinguistic2022, and are widely used [e.g., @petilli2021a]. Some of these covariates were highly intercorrelated ($r$ > .70), as shown below. To avoid the problem of multicollinearity, the maximum zero-order correlation allowed between any two covariates was of $r$ = $\pm$.70 [@dormannCollinearityReviewMethods2013; @harrison2018a]. In cases of higher correlations, the covariate with the largest effect in the model, based on the estimate ($\upbeta$), was selected.

In Studies 1 (semantic priming) and 2 (semantic decision), the lexical covariates were selected out of five variables, which mirrored those used by @wingfieldUnderstandingRoleLinguistic2022: namely, number of letters (i.e., orthographic length, which we computed in R), word frequency, number of syllables  [both the latter from @balota2007a], orthographic Levenshtein distance [@yarkoniMovingColtheartNew2008] and phonological Levenshtein distance [@suarezObservingNeighborhoodEffects2011]. In Study 3 (lexical decision), the procedure was identical except that word frequency could not be selected as a covariate because it constituted a predictor of interest, specifically corresponding to linguistic information (for details, see Study 3 in the main article).

@@

# Create table (using custom function from the 'R_functions' folder)
frequentist_model_table(
  KR_summary_lexical_covariates_selection_semanticpriming_lmerTest, 
  confidence_intervals = confint_lexical_covariates_selection_semanticpriming_lmerTest,
  caption = 'Mixed-effects model for the selection of lexical covariates in the semantic priming study.') %>% 
  # Place table close to designated position
  kable_styling(latex_options = 'HOLD_position') %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
                           'CI = confidence interval. By-participant random slopes were included for',
                           'every effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

@@

# Create table (using custom function from the 'R_functions' folder)
frequentist_model_table(
  KR_summary_lexical_covariates_selection_semanticdecision_lmerTest, 
  confidence_intervals = confint_lexical_covariates_selection_semanticdecision_lmerTest,
  caption = 'Mixed-effects model for the selection of lexical covariates in the semantic decision study.') %>% 
  # Place table close to designated position
  kable_styling(latex_options = 'HOLD_position') %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
                           'CI = confidence interval. By-participant random slopes were included for',
                           'every effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

@@

@@

# Create table (using custom function from the 'R_functions' folder)
frequentist_model_table(
  KR_summary_lexical_covariates_selection_lexicaldecision_lmerTest, 
  confidence_intervals = confint_lexical_covariates_selection_lexicaldecision_lmerTest,
  caption = 'Mixed-effects model for the selection of lexical covariates in the lexical decision study.') %>% 
  # Place table close to designated position
  kable_styling(latex_options = 'HOLD_position') %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored variables; \\\\textit{SE} = standard error;',
                           'CI = confidence interval. By-participant random slopes were included for',
                           'every effect.', 
                           # Begin lines after first one with a dot-sized indent
                           sep = ' \\\\linebreak \\\\phantom{.}'))

>>>>

# This appendix is rendered by the main manuscript. It inherits all the 
# parameters set in the main manuscript and the objects loaded therein.

@@

Lexical covariates are usually used in conceptual processing studies due to the widespread connections among lexical and semantic variables [e.g., @pexman2018a; @petilli2021a; @wingfieldUnderstandingRoleLinguistic2022]. Including these covariates---or nuisance variables---in the model allows a more rigorous analysis of the predictors of interest [@sassenhagenCommonMisapplicationStatistical2016]. In each of the present studies, the covariates were selected out of a group of five variables that had been used as covariates in @wingfieldUnderstandingRoleLinguistic2022, and are widely used [e.g., @petilli2021a]. Some of these covariates were highly intercorrelated ($r$ > .70), as shown below. To avoid the problem of multicollinearity, the maximum zero-order correlation allowed between any two covariates was of $r$ = $\pm$.70 [@dormannCollinearityReviewMethods2013; @harrison2018a]. In cases of higher correlations, the covariate with the largest effect in the model, based on the estimate ($\upbeta$), was selected.

In Studies 1 (semantic priming) and 2 (semantic decision), the lexical covariates were selected out of five variables, which mirrored those used by @wingfieldUnderstandingRoleLinguistic2022: namely, number of letters (i.e., orthographic length, which we computed in R), word frequency, number of syllables  [both the latter from @balota2007a], orthographic Levenshtein distance [@yarkoniMovingColtheartNew2008] and phonological Levenshtein distance [@suarezObservingNeighborhoodEffects2011; @yapVisualWordRecognition2009]. In Study 3 (lexical decision), the procedure was more particular, as it served two purposes. First, the variable that had the largest effect out of the five was selected as the language-based predictor of interest (see reason in [\underline{Study 3 in the main text}](#lexicaldecision)). Second, one variable was selected as a covariate among the remaining four.

@@

# Create table (using custom function from the 'R_functions' folder)
frequentist_model_table(
  KR_summary_lexical_covariates_selection_semanticpriming_lmerTest, 
  confidence_intervals = confint_lexical_covariates_selection_semanticpriming_lmerTest,
  caption = 'Mixed-effects model for the selection of lexical covariates in the semantic priming study.') %>% 
  # Place table close to designated position
  kable_styling(latex_options = 'hold_position') %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored predictors; \\\\textit{SE} = standard error;',
                           'CI = confidence interval. By-participant random slopes were included for',
                           'every effect.', 
                           # After first line in the footnote, begin next lines with a dot-sized indent to correct default error.
                           sep = ' \\\\linebreak \\\\phantom{.}'))

@@

# Create table (using custom function from the 'R_functions' folder)
frequentist_model_table(
  KR_summary_lexical_covariates_selection_semanticdecision_lmerTest, 
  confidence_intervals = confint_lexical_covariates_selection_semanticdecision_lmerTest,
  caption = 'Mixed-effects model for the selection of lexical covariates in the semantic decision study.') %>% 
  # Place table close to designated position
  kable_styling(latex_options = 'hold_position') %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored predictors; \\\\textit{SE} = standard error;',
                           'CI = confidence interval. By-participant random slopes were included for',
                           'every effect.', 
                           # After first line in the footnote, begin next lines with a dot-sized indent to correct default error.
                           sep = ' \\\\linebreak \\\\phantom{.}'))

@@

The selection model for Study 3 served a twofold purpose. First, the variable that had the largest effect out of the five was selected as the language-based predictor of interest (see reason in [\underline{Study 3 in the main text}](#lexicaldecision)). Second, one variable was selected as a covariate among the remaining four.

@@

# Create table (using custom function from the 'R_functions' folder)
frequentist_model_table(
  KR_summary_lexical_covariates_selection_lexicaldecision_lmerTest, 
  confidence_intervals = confint_lexical_covariates_selection_lexicaldecision_lmerTest,
  caption = 'Mixed-effects model for the selection of lexical covariates in the lexical decision study.') %>% 
  # Place table close to designated position
  kable_styling(latex_options = 'hold_position') %>%

  # Footnote describing abbreviations, random slopes, etc. 
  # LaTeX code used to format the text.
  footnote(escape = FALSE, threeparttable = TRUE, general_title = '\\\\linebreak', 
           general = paste('\\\\textit{Note}. $\\\\upbeta$ = Estimate based on $z$-scored predictors; \\\\textit{SE} = standard error;',
                           'CI = confidence interval. By-participant random slopes were included for',
                           'every effect.', 
                           # After first line in the footnote, begin next lines with a dot-sized indent to correct default error.
                           sep = ' \\\\linebreak \\\\phantom{.}'))

### 2022-09-26 manuscript/appendix-B-frequentist-analysis-diagnostics.Rmd
26092022

### The multiple-optimizers sanity check from `lme4::allFit()`

Framed within the drive to maintain random slopes wherever possible, the developers of the 'lme4' package propose a sanity check that uses a part of the 'lme4' *engine* called 'optimizer'. Every model has a default optimizer, unless a specific one is chosen through `control = lmerControl(optimizer = '...')` (in `lmer` models) or `control = glmerControl(optimizer = '...')` (in `glmer` models). The 7 widely-available optimizers are:

@@

To assess whether convergence warnings render the results invalid, or on the contrary, the results can be deemed valid in spite of the warnings, @batesPackageLme42021 suggest refitting models affected by convergence warnings with a variety of optimizers. The authors argue that if the different optimizers produce practically-equivalent results, the results are valid. For this purpose, the 'allFit' function from the 'lme4' package allows the refitting of models using a number of optimizers. To use the 7 optimizers listed above, two extra packages were installed: 'dfoptim' and 'optimx' (see [lme4 manual](https://cran.r-project.org/web/packages/lme4/lme4.pdf)). The output from 'allFit' contains several statistics on the fixed and the random effects fitted by each optimizer (see [example](https://github.com/lme4/lme4/issues/512#issue-425198940)).

@@

The residuals of the linear mixed-effects models in all three studies violated the assumption of normality. Even though linear mixed-effects models tend to be quite robust to deviations from normality [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020], we sought to verify our results. To this end, two robust models were performed in each study, as described below.

@@

In the initial model, the optimizer used (the default one in 'lmerTest') was '`r semanticpriming_lmerTest@optinfo$optimizer`', and the convergence warning read: '`r semanticpriming_lmerTest@optinfo$conv$lme4$messages`'.

Based on the reanalysis using 7 optimizers, Figure \@ref(fig:main-effects-semanticpriming-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-semanticpriming-allFit-convergence) shows the fixed interactions.

```{r main-effects-semanticpriming-allFit-convergence, fig.cap = 'Fixed, main effects from the semantic priming study fitted by 7 optimizers.'}

@@

```{r interactions-semanticpriming-allFit-convergence, fig.cap = 'Fixed interaction effects from the semantic priming study fitted by 7 optimizers.'}

@@

In the initial model, the optimizer used (the default one in 'lmerTest') was '`r semanticpriming_with_visualsimilarity_lmerTest@optinfo$optimizer`', and the convergence warning read: '`r semanticpriming_with_visualsimilarity_lmerTest@optinfo$conv$lme4$messages`'.

Based on the reanalysis using 7 optimizers, Figure \@ref(fig:main-effects-semanticpriming-with-visualsimilarity-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-semanticpriming-with-visualsimilarity-allFit-convergence) shows the fixed interactions.

```{r main-effects-semanticpriming-with-visualsimilarity-allFit-convergence, fig.cap = 'Fixed, main effects from the semantic priming study fitted by 7 optimizers.'}

@@

```{r interactions-semanticpriming-with-visualsimilarity-allFit-convergence, fig.cap = 'Fixed interaction effects from the semantic priming study fitted by 7 optimizers.'}

@@

In the initial model, the optimizer used (the default one in 'lmerTest') was '`r semanticdecision_lmerTest@optinfo$optimizer`', and the convergence warning read: '`r semanticdecision_lmerTest@optinfo$conv$lme4$messages`'.

Based on the reanalysis using 7 optimizers, Figure \@ref(fig:main-effects-semanticdecision-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-semanticdecision-allFit-convergence) shows the fixed interactions.

```{r main-effects-semanticdecision-allFit-convergence, fig.cap = 'Fixed, main effects from the semantic decision study fitted by 7 optimizers.'}

@@

```{r interactions-semanticdecision-allFit-convergence, fig.cap = 'Fixed interaction effects from the semantic decision study fitted by 7 optimizers.'}

@@

In the initial model, the optimizer used (the default one in 'lmerTest') was '`r lexicaldecision_lmerTest@optinfo$optimizer`', and the convergence warning read: '`r lexicaldecision_lmerTest@optinfo$conv$lme4$messages`'.

Based on the reanalysis using 7 optimizers, Figure \@ref(fig:main-effects-lexicaldecision-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-lexicaldecision-allFit-convergence) shows the fixed interactions.

```{r main-effects-lexicaldecision-allFit-convergence, fig.cap = 'Fixed, main effects from the lexical decision study fitted by 7 optimizers.'}

@@

```{r interactions-lexicaldecision-allFit-convergence, fig.cap = 'Fixed interaction effects from the lexical decision study fitted by 7 optimizers.'}

>>>>

### The multiple-optimisers sanity check from `lme4::allFit()`

Framed within the drive to maintain random slopes wherever possible, the developers of the 'lme4' package propose a sanity check that uses a part of the 'lme4' *engine* called 'optimiser'. Every model has a default optimiser, unless a specific one is chosen through `control = lmerControl(optimiser = '...')` (in `lmer` models) or `control = glmerControl(optimiser = '...')` (in `glmer` models). The seven widely-available optimisers are:

@@

To assess whether convergence warnings render the results invalid, or on the contrary, the results can be deemed valid in spite of the warnings, @batesPackageLme42021 suggest refitting models affected by convergence warnings with a variety of optimisers. The authors argue that if the different optimisers produce practically-equivalent results, the results are valid. For this purpose, the 'allFit' function from the 'lme4' package allows the refitting of models using a number of optimisers. To use the seven optimisers listed above, two extra packages were installed: 'dfoptim' and 'optimx' (see [lme4 manual](https://cran.r-project.org/web/packages/lme4/lme4.pdf)). The output from 'allFit' contains several statistics on the fixed and the random effects fitted by each optimiser (see [example](https://github.com/lme4/lme4/issues/512#issue-425198940)).

@@

The residuals of the linear mixed-effects models in the three studies violated the assumption of normality. Even though linear mixed-effects models tend to be quite robust to deviations from normality [@kniefViolatingNormalityAssumption2021; @schielzethRobustnessLinearMixed2020], we sought to verify our results. To this end, two robust models were performed in each study, as described below.

@@

In the initial model, the optimiser used (the default one in 'lmerTest') was '`r semanticpriming_lmerTest@optinfo$optimiser`', and the convergence warning read: '`r semanticpriming_lmerTest@optinfo$conv$lme4$messages`'.

Based on the reanalysis using seven optimisers, Figure \@ref(fig:main-effects-semanticpriming-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-semanticpriming-allFit-convergence) shows the fixed interactions.

```{r main-effects-semanticpriming-allFit-convergence, fig.cap = 'Fixed, main effects from the semantic priming study fitted by seven optimisers.'}

@@

```{r interactions-semanticpriming-allFit-convergence, fig.cap = 'Fixed interaction effects from the semantic priming study fitted by seven optimisers.'}

@@

In the initial model, the optimiser used (the default one in 'lmerTest') was '`r semanticpriming_with_visualsimilarity_lmerTest@optinfo$optimiser`', and the convergence warning read: '`r semanticpriming_with_visualsimilarity_lmerTest@optinfo$conv$lme4$messages`'.

Based on the reanalysis using seven optimisers, Figure \@ref(fig:main-effects-semanticpriming-with-visualsimilarity-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-semanticpriming-with-visualsimilarity-allFit-convergence) shows the fixed interactions.

```{r main-effects-semanticpriming-with-visualsimilarity-allFit-convergence, fig.cap = 'Fixed, main effects from the semantic priming study fitted by seven optimisers.'}

@@

```{r interactions-semanticpriming-with-visualsimilarity-allFit-convergence, fig.cap = 'Fixed interaction effects from the semantic priming study fitted by seven optimisers.'}

@@

In the initial model, the optimiser used (the default one in 'lmerTest') was '`r semanticdecision_lmerTest@optinfo$optimiser`', and the convergence warning read: '`r semanticdecision_lmerTest@optinfo$conv$lme4$messages`'.

Based on the reanalysis using seven optimisers, Figure \@ref(fig:main-effects-semanticdecision-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-semanticdecision-allFit-convergence) shows the fixed interactions.

```{r main-effects-semanticdecision-allFit-convergence, fig.cap = 'Fixed, main effects from the semantic decision study fitted by seven optimisers.'}

@@

```{r interactions-semanticdecision-allFit-convergence, fig.cap = 'Fixed interaction effects from the semantic decision study fitted by seven optimisers.'}

@@

In the initial model, the optimiser used (the default one in 'lmerTest') was '`r lexicaldecision_lmerTest@optinfo$optimiser`', and the convergence warning read: '`r lexicaldecision_lmerTest@optinfo$conv$lme4$messages`'.

Based on the reanalysis using seven optimisers, Figure \@ref(fig:main-effects-lexicaldecision-allFit-convergence) shows the fixed, main effects, and Figure \@ref(fig:interactions-lexicaldecision-allFit-convergence) shows the fixed interactions.

```{r main-effects-lexicaldecision-allFit-convergence, fig.cap = 'Fixed, main effects from the lexical decision study fitted by seven optimisers.'}

@@

```{r interactions-lexicaldecision-allFit-convergence, fig.cap = 'Fixed interaction effects from the lexical decision study fitted by seven optimisers.'}

### 2022-09-26 manuscript/appendix-C-Bayesian-analysis-diagnostics.Rmd
29062022
26092022

# This appendix inherits the libraries, the working directory and the
# data sets loaded in manuscript.Rmd, when the latter is knitted.

@@

This appendix presents diagnostics for the Bayesian analyses. In each study, prior predictive checks are presented before posterior predictive checks. Furthermore, in each of these checks, the models presented first have the default Gaussian distribution, whereas the next series have an exponentially modified Gaussian (dubbed 'ex-Gaussian') distribution with an identity link function (for details, see the section titled 'Distributions and prior predictive checks' in the main article). Eyeball estimation is used to assess the outcomes of these checks [for background on predictive checks and for alternative estimation procedures, see @gelmanPosteriorPredictiveAssessment1996; @moranPosteriorPredictiveNull2021; @schootBayesianStatisticsModelling2021]. One diagnostic not shown in this appendix is the $\widehat R$, which is shown in [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results) instead.

@@

Figures \@ref(fig:semanticpriming-priorpredictivecheck-informativepriors), \@ref(fig:semanticpriming-priorpredictivecheck-weaklyinformativepriors) and \@ref(fig:semanticpriming-priorpredictivecheck-diffusepriors) show the prior predictive checks for the Gaussian models. These plots show the maximum, mean and minimum values of the observed data ($y$) and those of the predicted distribution ($y_{rep}$, which stands for *rep*lications of the outcome). The way of interpreting these plots is by comparing the observed data to the predicted distribution. The specifics of this vary across the three plots in the series. Firstly, in the upper plot, which shows the maximum values, the ideal scenario would have the observed ($y$) value overlapping with the maximum value of the predicted distribution ($y_{rep}$). Secondly, in the middle plot, showing the mean values, the ideal scenario would show the observed ($y$) value overlapping with the mean value of the predicted distribution ($y_{rep}$). Lastly, in the lower plot, which shows the minimum values, the ideal scenario would have the observed ($y$) value overlapping with the minimum value of the predicted distribution ($y_{rep}$). The overlap need not be absolute but the closer the observed and the predicted values on the X axis, the better. As such, the three predictive checks below---corresponding to models that used the default Gaussian distribution---show that the priors fitted the data acceptably but not very well.

@@

Based on the above results, the ex-Gaussian distribution was used in the final models. Figure \@ref(fig:semanticpriming-posteriorpredictivechecks-allpriors-exgaussian) presents the posterior predictive checks the latter models. The interpretation of these plots is simple: the distributions of the observed ($y$) and the predicted data ($y_{rep}$) should be as similar as possible. As such, the plots below suggest that the results are trustworthy.

(ref:semanticpriming-posteriorpredictivechecks-allpriors-exgaussian) Posterior predictive checks for the (ex-Gaussian) models from the semantic priming study. $y$ = observed data; $y_{rep}$ = predicted data.

@@

Figures \@ref(fig:semanticdecision-priorpredictivecheck-informativepriors), \@ref(fig:semanticdecision-priorpredictivecheck-weaklyinformativepriors) and \@ref(fig:semanticdecision-priorpredictivecheck-diffusepriors) show the prior predictive checks for the Gaussian models (for background on these checks, see [\underline{Study 1 above}](#study1-bayesian-diagnostics)). The three plots---corresponding to models that used the default Gaussian distribution---show that the priors fitted the data acceptably but not very well.

@@

Figures \@ref(fig:lexicaldecision-priorpredictivecheck-informativepriors), \@ref(fig:lexicaldecision-priorpredictivecheck-weaklyinformativepriors) and \@ref(fig:lexicaldecision-priorpredictivecheck-diffusepriors) show the prior predictive checks for the Gaussian models (for background on these checks, see [\underline{Study 1 above}](#study1-bayesian-diagnostics)). The three plots---corresponding to models that used the default Gaussian distribution---show that the priors fitted the data acceptably but not very well.

>>>>

# This appendix is rendered by the main manuscript. It inherits all the 
# parameters set in the main manuscript and the objects loaded therein.

@@

This appendix presents diagnostics for the Bayesian analyses. In each study, prior predictive checks are presented before posterior predictive checks. Furthermore, in each of these checks, the models presented first have the default Gaussian distribution, whereas the next series have an exponentially modified Gaussian (dubbed 'ex-Gaussian') distribution with an identity link function (for details, see the section titled 'Distributions and prior predictive checks' in the main text). Eyeball estimation is used to assess the outcomes of these checks [for background on predictive checks and for alternative estimation procedures, see @gelmanPosteriorPredictiveAssessment1996; @moranPosteriorPredictiveNull2021; @schootBayesianStatisticsModelling2021]. One diagnostic not shown in this appendix is the $\widehat R$, which is shown in [\underline{Appendix E}](#appendix-E-Bayesian-analysis-results) instead.

@@

Figures \@ref(fig:semanticpriming-priorpredictivecheck-informativepriors), \@ref(fig:semanticpriming-priorpredictivecheck-weaklyinformativepriors) and \@ref(fig:semanticpriming-priorpredictivecheck-diffusepriors) show the prior predictive checks for the Gaussian models. These plots show the maximum, mean and minimum values of the observed data ($y$) and those of the predicted distribution ($y_{rep}$, which stands for *rep*lications of the outcome). The way of interpreting these plots is by comparing the observed data to the predicted distribution. The specifics of this comparison vary across the three plots. First, in the upper plot, which shows the maximum values, the ideal scenario would show the observed maximum value ($y$) overlapping with the maximum value of the predicted distribution ($y_{rep}$). Second, in the middle plot, showing the mean values, the ideal scenario would show the observed mean value ($y$) overlapping with the mean value of the predicted distribution ($y_{rep}$). Last, in the lower plot, which shows the minimum values, the ideal scenario would have the observed minimum value ($y$) overlapping with the minimum value of the predicted distribution ($y_{rep}$). While the overlap need not be absolute, the closer the observed and the predicted values are on the X axis, the better. As such, the three predictive checks below---corresponding to models that used the default Gaussian distribution---show that the priors fitted the data acceptably but not very well.

@@

Based on the above results, the ex-Gaussian distribution was used in the final models. Figure \@ref(fig:semanticpriming-posteriorpredictivechecks-allpriors-exgaussian) presents the posterior predictive checks for the latter models. The interpretation of these plots is simple: the distributions of the observed ($y$) and the predicted data ($y_{rep}$) should be as similar as possible. As such, the plots below suggest that the results are trustworthy.

(ref:semanticpriming-posteriorpredictivechecks-allpriors-exgaussian) Posterior predictive checks for the (ex-Gaussian) models from the semantic priming study. The observed data ($y$) and the predicted data ($y_{rep}$) almost entirely overlap with each other, demonstrating a very good fit.

@@

Figures \@ref(fig:semanticdecision-priorpredictivecheck-informativepriors), \@ref(fig:semanticdecision-priorpredictivecheck-weaklyinformativepriors) and \@ref(fig:semanticdecision-priorpredictivecheck-diffusepriors) show the prior predictive checks for the Gaussian models (for background on these checks, see [\underline{Study 1}](#study1-bayesian-diagnostics)). The three plots---corresponding to models that used the default Gaussian distribution---show that the priors fitted the data acceptably but not very well.

@@

Figures \@ref(fig:lexicaldecision-priorpredictivecheck-informativepriors), \@ref(fig:lexicaldecision-priorpredictivecheck-weaklyinformativepriors) and \@ref(fig:lexicaldecision-priorpredictivecheck-diffusepriors) show the prior predictive checks for the Gaussian models (for background on these checks, see [\underline{Study 1}](#study1-bayesian-diagnostics)). The three plots---corresponding to models that used the default Gaussian distribution---show that the priors fitted the data acceptably but not very well.

### 2022-09-26 manuscript/appendix-D-interaction-plots.Rmd
26092022

This appendix presents plots of interactions that were not shown in the main text.

@@

(ref:semanticpriming-interactions-with-attentional-control) Interactions of attentional control with language-based similarity and visual-strength difference. Attentional control is constrained to deciles (ten sections) in this plot, whereas in the statistical analysis it contained more values within the current range. *n* = number of participants contained between decile values.

@@

```{r semanticpriming-interaction-word-concreteness-difference-SOA, fig.cap = 'Interaction of stimulus-onset asynchrony (SOA) with word-concreteness difference. SOA was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here.', out.width = '65%'}

@@

(ref:semanticpriming-interaction-word-concreteness-difference-vocabulary-size) Interaction of word-concreteness difference with vocabulary size. Vocabulary size is constrained to deciles in this plot, whereas in the statistical analysis it contained more values within the current range. *n* = number of participants contained between decile values.

```{r semanticpriming-interaction-word-concreteness-difference-vocabulary-size, fig.cap = '(ref:semanticpriming-interaction-word-concreteness-difference-vocabulary-size)', out.width = '85%'}

@@

(ref:semanticpriming-interaction-word-concreteness-difference-gender) Interaction of word-concreteness difference with gender. Gender was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here. *n* = number of participants contained between decile values.

```{r semanticpriming-interaction-word-concreteness-difference-gender, fig.cap = '(ref:semanticpriming-interaction-word-concreteness-difference-gender)', out.width = '65%'}

@@

(ref:semanticdecision-interactions-with-information-uptake) Interactions of information uptake with language-based similarity and visual-strength difference. Information uptake is constrained to deciles in this plot, whereas in the statistical analysis it contained more values within the current range. *n* = number of participants contained between decile values.

```{r semanticdecision-interactions-with-information-uptake, fig.cap = '(ref:semanticdecision-interactions-with-information-uptake)', out.width = '90%'}

@@

(ref:lexicaldecision-interaction-word-concreteness-vocabulary-age) Interaction of word concreteness with vocabulary age. Vocabulary age is constrained to sextiles (six sections) in this plot, whereas in the statistical analysis it contained more values within the current range. *n* = number of participants contained between sextile values.

```{r lexicaldecision-interaction-word-concreteness-vocabulary-age, fig.cap = '(ref:lexicaldecision-interaction-word-concreteness-vocabulary-age)', out.width = '85%'}

@@

(ref:lexicaldecision-interaction-word-concreteness-gender) Interaction of word concreteness with gender. Gender was analysed using $z$-scores, but for clarity, the variable is shown in its basic form here. *n* = number of participants contained between sextile values.

>>>>

Figures \@ref(fig:semanticpriming-interactions-with-attentional-control) -- \@ref(fig:lexicaldecision-interaction-word-concreteness-gender) present interactions that were not displayed in the main article. All interaction plots are based on the frequentist analysis.

@@

(ref:semanticpriming-interactions-with-attentional-control) Interactions of attentional control with language-based similarity (panel a) and with visual-strength difference (panel b). Attentional control is constrained to deciles (10 sections) in this plot, whereas in the statistical analysis it contained more values within the current range. $n$ = number of participants contained between deciles.

@@

```{r semanticpriming-interaction-word-concreteness-difference-SOA, fig.cap = 'Interaction between stimulus onset asynchrony (SOA) and word-concreteness difference. SOA was analysed using $z$-scores, but for clarity, the basic labels are used in the legend.', out.width = '70%'}

@@

(ref:semanticpriming-interaction-word-concreteness-difference-vocabulary-size) Interaction between word-concreteness difference and vocabulary size. Vocabulary size is constrained to deciles in this plot, whereas in the statistical analysis it contained more values within the current range. $n$ = number of participants contained between deciles.

```{r semanticpriming-interaction-word-concreteness-difference-vocabulary-size, fig.cap = '(ref:semanticpriming-interaction-word-concreteness-difference-vocabulary-size)', out.width = '90%'}

@@

(ref:semanticpriming-interaction-word-concreteness-difference-gender) Interaction between word-concreteness difference and gender. Gender was analysed using $z$-scores, but for clarity, the basic labels are used in the legend. $n$ = number of participants contained between deciles.

```{r semanticpriming-interaction-word-concreteness-difference-gender, fig.cap = '(ref:semanticpriming-interaction-word-concreteness-difference-gender)', out.width = '70%'}

@@

(ref:semanticdecision-interactions-with-information-uptake) Interactions of information uptake with word co-occurrence (panel a) and with visual strength (panel b). Information uptake is constrained to deciles in this plot, whereas in the statistical analysis it contained more values within the current range. $n$ = number of participants contained between deciles.

```{r semanticdecision-interactions-with-information-uptake, fig.cap = '(ref:semanticdecision-interactions-with-information-uptake)', out.width = '95%'}

@@

(ref:lexicaldecision-interaction-word-concreteness-vocabulary-age) Interaction between word concreteness and vocabulary age. Vocabulary age is constrained to sextiles (6 sections) in this plot, whereas in the statistical analysis it contained more values within the current range. $n$ = number of participants contained between sextiles.

```{r lexicaldecision-interaction-word-concreteness-vocabulary-age, fig.cap = '(ref:lexicaldecision-interaction-word-concreteness-vocabulary-age)', out.width = '90%'}

@@

(ref:lexicaldecision-interaction-word-concreteness-gender) Interaction between word concreteness and gender. Gender was analysed using $z$-scores, but for clarity, the basic labels are used in the legend. $n$ = number of participants contained between sextiles.
